Making Soup: Preparing and Validating Models of the Bacterial Cytoplasm for Molecular Simulation

### 2019-11-29 paper/rebuttal.txt

2) Figure 1A: Even though it is not of importance for the message
conveyed by this figure, this reviewer nonetheless wonders what the
difference between the red and green particles is in that figure. A
short note on it in the caption would be appreciated.

ANSWER: Red is water and green is biomolecules, this has been added to
the caption.

3) p. 13-15: It is mentioned that the RMSD of TufA, MetE and IcdA is
larger in the cytoplasm than in diluted solutions. Based on the RMSF
they also identified which part of these proteins become more
flexible. The authors later speculate that this is due to some
nonspecific interactions. Here, some more analysis is required. The
authors should demonstrate that these changes indeed arise from such
kind of interactions and not more specific interactions. And why are
only certain loops of each protein involved while all other loops seem
almost unaffected. And why does the RMSF of residues 450-460 of MetE
decrease?

ANSWER: As explained in the text, the region comprised by residues 40-62 of TufA is a conformational switch that is known to be flexible, residues 450-460 of MetE are a flexible loop and residues 1-8 of IcdA is a flexible coil. Thus, one can expect these regions to display variable conformational dynamics under different conditions. We removed the speculation about the unspecific interactions and the discussion about the RMSF difference (please see the answer to the next answer for details about this).

@@

4) Figure 5: Why are the standard errors of the RMSF for CspC so much
larger than for the other systems. Please comment.

ANSWER: Thank you for pointingt that out. There was a mistake in the statistics of our RMSF calculations.
We corrected it and updated the RMSF plots. The errors are much smaller now and the overall shift towards higher RMSF values for the proteins cytoplasm models is no longer present. Accordingly, the following sentences were removed from the text:

"In most cases (TufA, MetE, AhpC, CspC and Ppa), the residue-wise RMSF values are higher in the cytoplasm model than under diluted conditions, which indicates that proteins are more flexible in the cytoplasm model (Fig.~\ref{fig:rmsf}). This is in agreement with computational and experimental data showing that nonspecific interactions with crowders can lead to destabilization of proteins~\cite{Feig2011, miklos2011, Wang2012b}." from the results section.

" and the flexibility profiles calculated considering the C$\upalpha$ for each
chain of the elements of our cytoplasm model show that, in the crowded
condition, most of the proteins (TufA, MetE, AhpC, CspC and Ppa) are
more flexible than in the dilute condition (Fig.~\ref{fig:rmsf})." from the conclusion section.

"and \ref{fig:rmsf})" was removed from "the proteins are slightly less stable
in the cytoplasm model than in dilute condition (Figures
\ref{fig:structural_integrity_chain} and \ref{fig:rmsf})." in the conclusion section

### 2019-11-29 paper/virtual_cytoplasm_v2.tex
answers to referees

In most cases (TufA, MetE, AhpC, CspC and Ppa), the residue-wise RMSF values are higher in the cytoplasm model than under diluted conditions, which indicates that proteins are more flexible in the cytoplasm model (Fig.~\ref{fig:rmsf}). This is in agreement with computational and experimental data showing that nonspecific interactions with crowders can lead to destabilization of
proteins~\cite{Feig2011, miklos2011, Wang2012b}.

@@

Three crowders (TufA, MetE and IcdA) displayed greater deviation from
their crystallographic structure in the cytoplasm model when compared
to the dilute condition, indicating that there was some degree of
local unfolding
(Fig.~\ref{fig:structural_integrity_chain}A). Interestingly, oligomers
were marginally less stable in the cytoplasm model than in the dilute
condition.  (Fig.~\ref{fig:structural_integrity_chain}B) and the
flexibility profiles calculated considering the C$\upalpha$ for each
chain of the elements of our cytoplasm model show that, in the crowded
condition, most of the proteins (TufA, MetE, AhpC, CspC and Ppa) are
more flexible than in the dilute condition (Fig.~\ref{fig:rmsf}). This
is in agreement with previous simulations~\cite{Feig2011} and
experiment~\cite{miklos2011,Wang2012b} showing that crowders can
destabilize the native structure of proteins due to the numerous
unspecific short-lived interactions that are formed between them in a
crowded environment. A study of protein properties at increasing
concentration showed only few interactions between proteins of the
same type~\cite{Bashardanesh2019a}. The only specific interaction we
antecipate between the components of our cytoplasm model is between
TufA and tRNA (PDB ID 1TTT is an example of such
complex)~\cite{nissen1995crystal}. The TufA-tRNA complex is not
present in our simulation boxes even after \SI{1}{\micro\second} of
simulation starting from random orientations.

@@

We submitted this model to a total of \SI{3}{\micro\second} of
molecular dynamics simulations using a modified Amber99sb force
field that was tuned to reproduce experimental data of systems
composed of several macromolecules~\cite{Best2014a}. The model was
validated by comparing to experimental data about the reduction of the
translational diffusion coefficient of proteins in the cytoplasm of
\textit{E. coli} when compared to the dilute condition (Figure
\ref{fig:translational_diffusion})~\cite{Elowitz1999,Konopka2006}. Additionally,
our data is in agreement with recent simulation work and experimental data
that show that the unspecific interactions between macromolecules in a
crowded environment can destabilize
them~\cite{Feig2011,miklos2011,Wang2012b}. Specifically, we can see
that, despite the overall stability of our cytoplasm model even in the
\SI{}{\micro\second} timescale, the proteins are slightly less stable
in the cytoplasm model than in dilute condition (Figures
\ref{fig:structural_integrity_chain} and \ref{fig:rmsf}).

@@

\begin{acknowledgement}
The Swedish research council is acknowledged for a grant of computer time
(SNIC2018-2-42) through the High Performance Computing
Center North in Ume{\aa}, Sweden. Funding from eSSENCE - The e-Science
Collaboration (Uppsala-Lund-Ume{\aa}, Sweden) is gratefully acknowledged.
\end{acknowledgement}

>>>>

@@

Three crowders (TufA, MetE and IcdA) displayed greater deviation from
their crystallographic structure in the cytoplasm model when compared
to the dilute condition, indicating that there was some degree of
local unfolding
(Fig.~\ref{fig:structural_integrity_chain}A). Interestingly, oligomers
were marginally less stable in the cytoplasm model than in the dilute
condition  (Fig.~\ref{fig:structural_integrity_chain}B). This
is in agreement with previous simulations~\cite{Feig2011} and
experiment~\cite{miklos2011,Wang2012b} showing that crowders can
destabilize the native structure of proteins due to the numerous
unspecific short-lived interactions that are formed between them in a
crowded environment. A study of protein properties at increasing
concentration showed only few interactions between proteins of the
same type~\cite{Bashardanesh2019a}. The only specific interaction we
antecipate between the components of our cytoplasm model is between
TufA and tRNA (PDB ID 1TTT is an example of such
complex)~\cite{nissen1995crystal}. The TufA-tRNA complex is not
present in our simulation boxes even after \SI{1}{\micro\second} of
simulation starting from random orientations.

@@

We submitted this model to a total of \SI{3}{\micro\second} of
molecular dynamics simulations using a modified Amber99sb force
field that was tuned to reproduce experimental data of systems
composed of several macromolecules~\cite{Best2014a}. The model was
validated by comparing to experimental data about the reduction of the
translational diffusion coefficient of proteins in the cytoplasm of
\textit{E. coli} when compared to the dilute condition (Figure
\ref{fig:translational_diffusion})~\cite{Elowitz1999,Konopka2006}. Additionally,
our data is in agreement with recent simulation work and experimental data
that show that the unspecific interactions between macromolecules in a
crowded environment can destabilize
them~\cite{Feig2011,miklos2011,Wang2012b}. Specifically, we can see
that, despite the overall stability of our cytoplasm model even in the
\SI{}{\micro\second} timescale, the proteins are slightly less stable
in the cytoplasm model than in dilute condition (Figures
\ref{fig:structural_integrity_chain}.

@@

\begin{acknowledgement}
The Swedish research council is acknowledged for a grant of computer time
(SNIC2018-2-42) through the High Performance Computing
Center North in Ume{\aa}, Sweden. Funding from eSSENCE - The e-Science
Collaboration (Uppsala-Lund-Ume{\aa}, Sweden) and FAPESP - S{\~a}o Paulo Research Foundation (grants 2013/00927-7 and 2016/04958-2) are gratefully acknowledged.
\end{acknowledgement}
